\documentclass[10pt,a4paper,sans]{moderncv}     

% modern themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

% character encoding
\usepackage[utf8]{inputenc} 

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

\usepackage{import}

% #######################  PERSONAL DATA #######################
\name{Ricardo}{Mutti\\\vspace{10pt}}
\title{{\fontsize{18}{10} \selectfont Big Data Engineer | Software Engineer} {\fontsize{22}{10} \selectfont | \vspace{10pt}}}
\address{Rua Santa Albina, 22}{05518-000}{São Paulo - Brazil}
\phone[mobile]{+55 (11) 97308-3737}
\email{rc.mutti@gmail.com}
\homepage{https://www.linkedin.com/in/ricardo-mutti-a18131b7/}

\begin{document}

% #######################  QUOTE #######################
\makecvtitle
\small{"In fifteen years we'll be teaching programming just like reading and writing and wondering why we didn't do it sooner" - Zuckerberg, Mark.}
\vspace{6pt}

% #######################  WORK HISTORY #######################
\section{Work History}
\vspace{6pt}

\begin{itemize}

\item{\cventry{May 2018 -- Current}{Lead Big Data Engineer - Associate Director}{\href{https://parceirosoyo.com.br}{BTG Pactual}}{São Paulo, Brazil}{}{\vspace{10pt}
BTG Pactual is the largest investment bank in Latin America. Upon my arrival on BTG I worked on building the foundations of a Data Analytics team.\\
My first project was to create a centralized Data Lake for BTG Pactual Digital, the new online banking business, accounting for all possible information of our customers as well as presenting the ultimate source for our digital marketing strategies and business KPIs. I worked for one year in this project.\\
After that I led another project with similar characteristics. I created a new Data Lake comprising financial market information and oversaw its operations while leading a team of six Data Engineers. Ultimately achieving the goal of democratizing data access throughout the corporation and promoting an environment for quantitative analysis.\\
All in all, during my experience at BTG, I acquired expertise in managing big loads of data, whilst achieving cost effectiveness, optimal processing time and low maintenance status.\\
Main Stack: Nifi, S3, Airflow, EMR, Pyspark, Parquet, Glue, Athena, DynamoDB, ECS, AWS Lambda and SQS.}}
\vspace{10pt}

\item{\cventry{Jan 2016 -- May 2018}{Software Engineer}{\href{https://www.appsimples.com.br}{AppSimples}}{São Paulo, Brazil}{}{\vspace{10pt}Appsimples is a software house start-up, aiming at solving real world problems through technology. I was one of the first employees and worked there for almost 3 years, in a variety of projects and stacks. \\
I worked with Android apps, iOS apps, websites in ReactJS and even IoT. \\
My time there taught me to easily learn new technologies and programming languages while writing clean, well documented and easy to maintain code.\\
Main Stack: Swift 3, Java, Android, iOS, ReactJS, NodeJS, AWS Lambda and DynamoDB.}}
\vspace{6pt}

\end{itemize}

% #######################  EDUCATION #######################
\section{Education}
\vspace{6pt}

\subsection{Academic Qualifications}
\vspace{6pt}

\begin{itemize}

\item{\cventry{2012--2016}{Mechatronic Engineering}{Polytechnic School of the University of São Paulo}{São Paulo}{}{}}
\vspace{6pt}

% \item{\cventry{2010--2011}{Preparatory course}{Anglo Sergipe}{São Paulo}{}{}}
% \item{\cventry{2002--2009}{Regular}{Porto Seguro High Schol}{São Paulo}{}{}}

\end{itemize}

% #######################  CERTIFICATIONS #######################
\subsection{Certifications}
\vspace{6pt}

\begin{itemize}

\item{\cventry{May 2018}{\href{https://neuralmind.ai/en/home-en/}{NeuralMind}}{Deep Learning in Practice}{}{}{}}
\vspace{6pt}

\item{\cventry{Aug 2017}{Udemy}{Modern React with Redux}{}{}{}}
\vspace{6pt}

\item{\cventry{May 2017}{Lynda.com}{Swift 3 Essential Training}{}{}{}}
\vspace{6pt}

\item{\cventry{May 2016}{Code School}{Shaping up with Angular.js}{}{}{}}
\vspace{6pt}

\end{itemize}

% #######################  NOTABLE PROJECTS #######################
\section{Notable Projects}
\vspace{6pt}

\begin{itemize}

\item{\cventry{Jun 2019}{{Slides 43-52}}{\href{https://pt.slideshare.net/AmazonWebServices/secure-your-data-lake-a-financial-industry-perspective-svc203-so-paulo-aws-summit}{BTG Data Lake on AWS}}{}{}{}}
\vspace{6pt}

\item{\cventry{Jan 2018}{{All Versions}}{\href{https://play.google.com/store/apps/details?id=br.com.letsee.cliente}{LeetSee}}{}{}{}}
\vspace{6pt}

\item{\cventry{May 2017}{{Version 2.8 to 4.0 (total: 7)}}{\href{https://apps.apple.com/br/app/quintoandar-im\%C3\%B3veis/id1109011232}{Quinto Andar}}{}{}{}}
\vspace{6pt}

\end{itemize}

% #######################  TECHNICAL SKILLS #######################
\section{Technical Skills}
\vspace{6pt}

\begin{itemize}

\item \textbf{Programming Languages:} Python, Java, Swift 3.0, Javascript, Typescript, HTML, CSS.
\vspace{6pt}

\item \textbf{Web Developer:} NodeJS (Advanced), Material UI (Intermediate), Serverless (Advanced), ReactJS (Intermediate), Webpack (Intermediate).
\vspace{6pt}

\item \textbf{Big Data:} Nifi, Airflow, Pyspark, Hive, Pandas, Pyarrow, Parquet, Ganglia, Hue, Plotly.
\vspace{6pt}

\item \textbf{Tools:} Jupyter, Pycharm, Jira, Alfred, VSCode, iTerm(.zsh), Slack, Github, GitLab, Android Studio.
\vspace{6pt}

\item \textbf{AWS resources:} EMR (Advanced), S3 (Advanced), Athena (Advanced), Glue Catalog(Advanced), Lambda (Advanced), Route 53 (Advanced),  Gateway (Advanced), EC2 (Advanced), Dynamo (Intermediate), CloudFront (Intermediate).
\vspace{6pt}

\item \textbf{General Skills:} Good git and CI/CD skills, works well with Scrum.
\vspace{6pt}

\item \textbf{Other:} Cloud security, market data knowledge, familiarity with Apple and Google Stores, good Firebase skills, Colemak adept.
\vspace{6pt}

\end{itemize}

% #######################  LANGUAGES #######################
\section{Languages}
\vspace{6pt}

\begin{itemize}

\item \textbf{Portugues:} Native.
\vspace{6pt}

\item \textbf{English:} Advanced.
\vspace{6pt}

\item \textbf{Spanish:} Basic.
\vspace{6pt}

\end{itemize}

% #######################  WEBSITES #######################
\section{Websites}
\vspace{6pt}

\begin{itemize}

\item \textbf{Stack Overflow: }\href{https://stackoverflow.com/users/5848237/ricardo-mutti?tab=profile}{Ricardo Mutti}
\vspace{6pt}

\item \textbf{Github: }\href{https://github.com/Ricardo-Mutti}{Ricardo-Mutti}
\vspace{6pt}

\end{itemize}

% #######################  END DOCUMENT #######################
\end{document}